### 2025-04-17 multiple-regression.qmd
20250417 - spread-level plot

To evaluate homoscedasticity, we can evaluate residual plots (@fig-residualPlots).
In residual plots, homoscedasticity is identified as a constant spread of residuals versus fitted values—the residuals do not show a fan or cone shape.
If there is heteroscedasticity, it may be necessary to transform the [outcome variable](#sec-correlationalStudy) to be more normally distributed.

@@

To evaluate homoscedasticity, we can evaluate residual plots (@fig-residualPlots).
In residual plots, you want a constant spread of residuals versus fitted values—you do not want the residuals to show a fan or cone shape.

@@

@@

The residual plots are in @fig-residualPlotsOutcomeTransformed.

@@

>>>>

To evaluate homoscedasticity, we can evaluate a residual plot (@fig-residualPlots) and spread-level plot (@fig-spreadLevelPlot).
A residual plot depicts the residuals on the y-axis as a function of the model's fitted values on the x-axis.
Homoscedasticity in a residual plot is identified as a constant spread of residuals versus fitted values—the residuals do not show a fan or cone shape; a fan or cone shape indicates heteroscedasticity.
A spread-level plot depicts the log of the absolute value of studentized residuals on the y-axis as a function of the log of the model's fitted values on the x-axis.
Homoscedasticity in a spread-level plot is identified as a flat slope; a slope that differs from zero indicates heteroscedasticity.

If there is heteroscedasticity, it may be necessary to transform the [outcome variable](#sec-correlationalStudy) to be more normally distributed.
The spread-level plot provides a suggested power transformation to transform the [outcome variable](#sec-correlationalStudy) so that the spread of residuals becomes more uniform across the fitted values.

@@

To evaluate homoscedasticity, we can evaluate a residual plot (@fig-residualPlots) and spread-level plot (@fig-spreadLevelPlots).
In a residual plot, you want a constant spread of residuals versus fitted values—you do not want the residuals to show a fan or cone shape.

@@

In a spread-level plot, you want a flat (zero) slope—you do not want a positive or negative slope.

```{r}
#| label: fig-spreadLevelPlot
#| fig-cap: "Spread-Level Plot."
#| fig-alt: "Spread-Level Plot."

car::spreadLevelPlot(
  quadraticTermsRegressionModel,
  id = TRUE)
```

@@

The residual plot is in @fig-residualPlotsOutcomeTransformed.

@@

The spread-level plot is in @fig-spreadLevelPlotOutcomeTransformed.

```{r}
#| label: fig-spreadLevelPlotOutcomeTransformed
#| fig-cap: "Spread-Level Plot After Transformation of Fantasy Points."
#| fig-alt: "Spread-Level Plot After Transformation of Fantasy Points."

car::spreadLevelPlot(
  linearRegressionModel_outcomeTransformed,
  id = TRUE)
```
